---
title: "Project-R-STAT412"
author: "Yon Garber"
date: "11/21/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rgeos)
library(rworldmap)
library(tidyverse)

# get world map
wmap <- getMap(resolution="high")

# get centroids
centroids <- gCentroid(wmap, byid=TRUE)

# get a data.frame with centroids
df <- as.data.frame(centroids)
head(df)
write.csv(df,'country_location.csv')
```
    Latitude = y,
    Longtitude = x
    
```{r}

df %>%
  mutate(abs_lat= abs(y))->
  df
```

```{r}
continent <- read_csv("countryContinent.csv")
location <- read_csv("country_location_to_use.csv")
suicide<- read_csv("Suicide.csv")
country_continent_join <-inner_join(location,continent, by="Country")
All_datasets_Suicide <- inner_join(suicide,country_continent_join, by="Country")
```
```{r}

All_datasets_Suicide %>%
spread(key = "Sex", value = "SUM")->
  df_Regression

All_datasets_Suicide
df_Regression
```
```{r}
df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Europe")%>%
  drop_na(`Both sexes`)->
  Y_Reg
y<- Y_Reg$`Both sexes`

x<-Y_Reg$Latitude
x1 <- Y_Reg$Longtitude

Regression_Europe_long <- lm(y~x1)

regression_Europe<- lm(y ~x)

ggplot(Y_Reg,aes(x=Latitude,y=`Both sexes`))+
  geom_point()+
  geom_smooth(method= lm, se=FALSE)+
  xlab("Latitude ")+
  ylab("Suicide rate per 100000 for both sexes")
```
scatter plot of x and y as longtitude and latitude and add the suicide rate as a color.
```{r} 
ggplot(Y_Reg,aes(x=Longtitude,y=Latitude, color=`Both sexes`))+
  geom_point()+
  xlab("Longitude")+
  ggtitle("Suicide rate map for Europe")+
  theme_bw()

```

```{r} 
df_Regression%>%
  group_by(Country)%>%
  drop_na(`Both sexes`)%>%
  mutate(abs_latit= abs(Latitude))->
  world_both_sexes

ggplot(world_both_sexes,aes(x=Longtitude,y=Latitude, color=`Both sexes`))+
  geom_point()+
  xlab("Longitude")+
  ggtitle("Suicide rate map for the world")+
  theme_bw()

world_regression <- lm(world_both_sexes$`Both sexes`~world_both_sexes$abs_latit)
```
```{r}
df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Asia")%>%
  drop_na(`Both sexes`)->
  Asia_both_sexes

ggplot(Asia_both_sexes,aes(x=Longtitude,y=Latitude, color=`Both sexes`))+
  geom_point()+
  xlab("Longitude")+
  ggtitle("Suicide rate map for Asia")+
  theme_bw()

```

```{r}
df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Americas")%>%
  drop_na(`Both sexes`)->
  Americas_both_sexes

ggplot(Americas_both_sexes,aes(x=Longtitude,y=Latitude, color=`Both sexes`))+
  geom_point()+
  xlab("Longitude")+
  ggtitle("Suicide rate map for Americas")+
  theme_bw()

```
```{r}
df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Africa")%>%
  drop_na(`Both sexes`)->
  Africa_both_sexes

ggplot(Africa_both_sexes,aes(x=Longtitude,y=Latitude, color=`Both sexes`))+
  geom_point()+
  xlab("Longitude")+
  ggtitle("Suicide rate map for Africa")+
  theme_bw()

```
```{r}
df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Oceania")%>%
  drop_na(`Both sexes`)->
  Oceania_both_sexes

ggplot(Oceania_both_sexes,aes(x=Longtitude,y=Latitude, color=`Both sexes`))+
  geom_point()+
  xlab("Longitude")+
  ggtitle("Suicide rate map for Oceania")+
  theme_bw()

```
now after doing mapping per continent and the world we check if there is any difference between the amount of men killing themselves in europe to women killing themselves in europe.

We found the ratio for each country and we have DF for each continent.
## Europe-
```{r}
df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Europe")%>%
  drop_na(Female)%>%
  ungroup()%>%
  summarize(Female_sum=sum(Female))->
  Europe_Female

df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Europe")%>%
  drop_na(Male)%>%
  ungroup()%>%
  summarize(Male_sum=sum(Male))->
  Europe_Male
```

## World-
```{r}
df_Regression %>%
  group_by(Country) %>%
  drop_na(Female)%>%
  ungroup()%>%
  summarize(Female_sum=sum(Female))->
  World_Female

df_Regression %>%
  group_by(Country) %>%
  drop_na(Male)%>%
  ungroup()%>%
  summarize(Male_sum=sum(Male))->
  World_Male
```

## Asia-
```{r}
df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Asia")%>%
  drop_na(Female)%>%
  ungroup()%>%
  summarize(Female_sum=sum(Female))->
  Asia_Female

df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Asia")%>%
  drop_na(Male)%>%
  ungroup()%>%
  summarize(Male_sum=sum(Male))->
  Asia_Male
```

## Africa-
```{r}
df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Africa")%>%
  drop_na(Female)%>%
  ungroup()%>%
  summarize(Female_sum=sum(Female))->
  Africa_Female

df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Africa")%>%
  drop_na(Male)%>%
  ungroup()%>%
  summarize(Male_sum=sum(Male))->
  Africa_Male
```

## America-
```{r}
df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Americas")%>%
  drop_na(Female)%>%
  ungroup()%>%
  summarize(Female_sum=sum(Female))->
  Americas_Female

df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Americas")%>%
  drop_na(Male)%>%
  ungroup()%>%
  summarize(Male_sum=sum(Male))->
  Americas_Male
```

## Oceania-
```{r}
df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Oceania")%>%
  drop_na(Female)%>%
  ungroup()%>%
  summarize(Female_sum=sum(Female))->
  Oceania_Female

df_Regression %>%
  group_by(Country) %>%
  filter(continent=="Oceania")%>%
  drop_na(Male)%>%
  ungroup()%>%
  summarize(Male_sum=sum(Male))->
  Oceania_Male
```
Now we will do the ratio for each country and plot it using latitude and longtitude adding color for the ratio-

```{r}
df_Regression %>%
  group_by(Country) %>%
  drop_na(Female)%>%
  select(Country, Female, Latitude, Longtitude, continent, sub_region)->
  World_Female_join

df_Regression %>%
  group_by(Country) %>%
  drop_na(Male)%>%
  select(Country, Male, Latitude, Longtitude, continent, sub_region)->
  World_Male_join

World_join<- inner_join(World_Male_join,World_Female_join,by='Country')

World_join %>%
  mutate(Ratio_Male_to_Female= Male/Female)->
  World_join

ggplot(World_join,aes(x=Longtitude.x,y=Latitude.x, color=Ratio_Male_to_Female))+
  geom_point()+
  xlab("Longitude")+
  ylab("Latitude")+
  ggtitle("World map of the ratio between men and women")


```
We should repeat the procedure above for each continent and then do the analysis by age+ make the presentation.
```{r}
World_join%>%
  group_by(Country)%>%
  filter(continent.y=="Europe")->
  world_join_Europe

  ggplot(world_join_Europe,aes(x=Longtitude.x,y=Latitude.x, color=Ratio_Male_to_Female))+
    geom_point()+
    xlab("Longitude")+
    ylab("Latitude")+
    ggtitle("Europe VS the ratio between men and women")

```
```{r}
World_join%>%
  group_by(Country)%>%
  filter(continent.y=="Asia")->
  world_join_Asia

  ggplot(world_join_Asia,aes(x=Longtitude.x,y=Latitude.x, color=Ratio_Male_to_Female))+
    geom_point()+
    xlab("Longitude")+
    ylab("Latitude")+
    ggtitle("Asia VS the ratio between men and women")
```
```{r}
World_join%>%
  group_by(Country)%>%
  filter(continent.y=="Americas")->
  world_join_Americas

  ggplot(world_join_Americas,aes(x=Longtitude.x,y=Latitude.x, color=Ratio_Male_to_Female))+
    geom_point()+
    xlab("Longitude")+
    ylab("Latitude")+
    ggtitle("Americas VS the ratio between men and women")
```
```{r}
World_join%>%
  group_by(Country)%>%
  filter(continent.y=="Oceania")->
  world_join_Oceania

  ggplot(world_join_Oceania,aes(x=Longtitude.x,y=Latitude.x, color=Ratio_Male_to_Female))+
    geom_point()+
    xlab("Longitude")+
    ylab("Latitude")+
    ggtitle("Oceania VS the ratio between men and women")
```
```{r}
World_join%>%
  group_by(Country)%>%
  filter(continent.y=="Africa")->
  world_join_Africa

  ggplot(world_join_Africa,aes(x=Longtitude.x,y=Latitude.x, color=Ratio_Male_to_Female))+
    geom_point()+
    xlab("Longitude")+
    ylab("Latitude")+
    ggtitle("Africa VS the ratio between men and women")
```





